Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-11 vesicle_code/docs/adhesion/adhesion.tex
changes by yny on Feb 11

Then, as the doublet
starts to rotate, each vesicle experiences drag force from both up and down diverging streaming flows.
For small extensional rate, the rotation will continue until $\theta = \pi$ so the doublet remains perfectly symmetric
with respect to their mid-plane  and each vesicle experiences drag forces that cancel in both directions.
For slightly higher extensional rate, we observe that the two vesicles slide against each other as the doublet rotate.
The slight sliding motion leads to a transition in the contact region membrane shape from a bulging profile to a sigmoidal profile of nearly uniform height.
This adjustment greatly reduces the net force on each vesicle, leading to an equilibrium configuration with an inclination angle $\theta < \pi$ as shown in 
the left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally,
the vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A = 0.7$,
  the extensional rate is $\chi = 0.7$, the adhesion length scale is
  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}
\end{figure}

>>>>

Then, as the doublet
starts to rotate, each vesicle experiences drag force from both up and down diverging streaming flows.
For small extensional rate, the rotation will continue until $\theta = \pi$ so the doublet remains perfectly symmetric
with respect to their mid-plane  and each vesicle experiences drag forces that cancel in both directions.
For slightly higher extensional rate, we observe that the two vesicles slide against each other as the doublet rotate.
The slight sliding motion leads to a transition in the contact region membrane shape from a bulging profile to 
an S-shape profile of nearly uniform height except near the edge of contact region.
This adjustment greatly reduces the net force on each vesicle, leading to an equilibrium configuration with an inclination angle $\theta < \pi$ as shown in 
the left of Figure~\ref{fig:extensionalInclinationAngle}.  Finally,
the vorticity and the flow between the vesicles approaches zero and the
result is a fluid trap containing the doublet.
\begin{figure}[htp]
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity01.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity02.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity03.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity04.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity05.png} \\
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity06.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity07.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity08.png}
  \includegraphics[height = 0.26\textwidth,trim={6cm 1cm 5cm
  0cm},clip]{figs/extensionalVorticity09.png}
  \includegraphics[height = 0.26\textwidth,trim={5cm 1cm 2cm
  0cm},clip]{figs/extensionalVorticity10.png}
  \caption{\label{fig:extensionalVorticity} The vorticity and total
  force of two vesicles in a doublet.  The reduced area is $\Delta A = 0.7$,
  the extensional rate is $\chi = 0.7$, the adhesion length scale is
  $\delta = 0.4$, and the Hamaker constant is $\mathcal{H} = 0.7$.}
\end{figure}
